---
title: "R Practice: Mapping Countries in Europe"
author: "Sylvia de Boer"
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

# R Practice: Mapping Countries in Europe
##### Sylvia de Boer
##### GIS III


#### Version of R and MacOS used:
    platform       x86_64-apple-darwin15.6.0   
    arch           x86_64                      
    os             darwin15.6.0                
    system         x86_64, darwin15.6.0        
    status                                     
    major          3                           
    minor          6.3                         
    year           2020                        
    month          02                          
    day            29                          
    svn rev        77875                       
    language       R                           
    version.string R version 3.6.3 (2020-02-29)
    nickname       Holding the Windsock  


#### Goal
    By following these instructions, I mapped the places in Europe I have visited.
    
    
#### Required Packages
    Given that they are already installed, you can refresh the libraries below in order to access the map we will be using.

```{r, results="hide"}
library(sf)
library(raster)
library(spData)
library(spDataLarge)
```


#### Coding
Here, we bring up the map of the world that we downloaded earlier through the packages we installed. Note that we're ordering by "name_long", which is why each country is a different color.
```{r eval=TRUE}
plot(world["name_long"], reset = TRUE)
```
In this next step, we'll identify the countries within the map that we'll need later.
```{r eval=TRUE}
germany = world[world$name_long == "Germany", ]
italy = world[world$name_long == "Italy", ]
netherlands = world[world$name_long == "Netherlands", ]
czechrepublic = world[world$name_long == "Czech Republic", ]
spain = world[world$name_long == "Spain", ]
unitedkingdom = world[world$name_long == "United Kingdom", ]
belgium = world[world$name_long == "Belgium", ]
france = world[world$name_long == "France", ]
europe = world[world$continent == "Europe", ]
```

Finally, we'll assign each country a different color.
```{r eval=TRUE}
plot(st_geometry(germany), col = "white", lwd = 3, main = "Places I've Visited in Europe", border = "lightgrey", expandBB = c(0.5, 0.2, 0.5, 0.2))
plot(st_geometry(world), lty = 3, add = TRUE, border = "grey")
plot(st_geometry(germany), col = "red", add = TRUE, border = "darkgrey")
plot(st_geometry(italy), col = "blue", add = TRUE, border = "darkgrey")
plot(st_geometry(netherlands), col = "orange", add = TRUE, border = "darkgrey")
plot(st_geometry(czechrepublic), col = "yellow", add = TRUE, border = "darkgrey")
plot(st_geometry(belgium), col = "purple", add = TRUE, border = "darkgrey")
plot(st_geometry(spain), col = "lightblue", add = TRUE, border = "darkgrey")
plot(st_geometry(france), col = "green", add = TRUE, border = "darkgrey")
plot(st_geometry(unitedkingdom), col = "pink", add = TRUE, border = "darkgrey")
```